\documentclass[a4paper,10pt]{article}
\usepackage[top=0.4in, bottom=0.6in, left=0.7in, right=0.7in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    urlcolor=black,
    linkcolor=black,
    citecolor=black
}
\usepackage{fontawesome}
\usepackage{parskip}

\titleformat{\section}{\bfseries\uppercase}{\thesection}{1em}{}
\titlespacing{\section}{0pt}{2pt}{-3pt}

% Global compact item spacing
\setlist[itemize]{leftmargin=1.5em, itemsep=0pt, topsep=2pt, parsep=0pt}

\begin{document}
\pagenumbering{gobble}

% === HEADER (CENTER ALIGNED) ===
\begin{center}
\textbf{\Huge Ashutosh Saxena} \\
\vspace{3pt}
\faPhone\ (+91) 8467935123 \quad
\faEnvelope\ \href{mailto:ashutosh.sx3010@gmail.com}{ashutosh.sx3010@gmail.com} \\
\faGlobe\ \href{https://www.ashutoshsaxena.space/}{Portfolio} \quad
\faLinkedin\ \href{https://www.linkedin.com/in/ashutosh-saxena-6b102925b/}{LinkedIn} \quad
\faGithub\ \href{https://github.com/ashutosh-sx/}{GitHub} \quad
\faCode\ \href{https://leetcode.com/u/Ashutosh_1030/}{LeetCode}
\end{center}

% === EDUCATION ===
\vspace{6pt}
\section*{Education}
\rule{\linewidth}{0.4pt}

\textbf{B.E. in Information Science and Engineering} \\
BMS Institute of Technology and Management, Bengaluru [2022 – 2026] \hfill CGPA: 8.92 

\textbf{Intermediate (PCM and Computer Science)} \\
Lucknow Public Schools and Colleges (ICSE) \hfill Grade: 95.75\%

% === PROJECTS ===
\vspace{6pt}
\section*{Projects}
\rule{\linewidth}{0.4pt}

\textbf{Travel Story Website – MERN Application} \hfill 
{\large \href{https://github.com/ashutosh-sx/tour_tracker}{\faGithub}} \\
\textit{Tech Stack: MongoDB, Express.js, React.js, Node.js, Tailwind CSS} 
\begin{itemize}[leftmargin=1.2em, itemsep=3pt, topsep=0pt, parsep=0pt]
  \item Created a full-stack MERN platform for recording and sharing travel stories with images and dates.
  \item Implemented RESTful APIs with JWT authentication for secure user and data management.  
  \item Developed a responsive React frontend with Tailwind CSS, integrated seamlessly with backend services.  
\end{itemize}

% \textbf{Varta Setu – Real-Time Chat Application} \hfill 
% {\large \href{http://vartasetu-web.vercel.app/}{\faGlobe} \hspace{6pt}%
% \href{https://github.com/ashutosh-sx/vartasetu-chatapp}{\faGithub}} \\
% \textit{Tech Stack: React.js, Next.js, Tailwind CSS, WebRTC, Socket.io} 
% \begin{itemize}
%   \item Developed a real-time chat application with multiple concurrent users and less than 10ms latency.
%   \item Secured 50+ user sessions using NextAuth with Google's authentication.
%   \item Implemented live user status and real-time notifications reducing missed messages by 80\%.
% \end{itemize}

% === EXPERIENCE ===
\vspace{6pt}
\section*{Experience}
\rule{\linewidth}{0.4pt}

\textbf{DELOAI PRIVATE LIMITED} \\
\textit{Web Developer Intern} \hfill \textit{July 2024 -- Nov 2024}
\begin{itemize}
  \item Built 5 production-grade web applications using JavaScript, React.js, and Node.js.
  \item Collaborated with cross-functional teams to deliver 10+ user-facing features.
  \item Worked in an Agile environment, delivering weekly sprints with a 95\% on-time completion rate.
\end{itemize}

\vspace{2pt}

\textbf{INTERFERON TECHNOLOGIES PRIVATE LIMITED} \\
\textit{Tech Lead -- Full Stack Developer Intern} \hfill \textit{Dec 2024 -- Dec 2025}
\begin{itemize}
   \item Led the development of neetxcel.com~\href{https://neetxcel.com/}{\faExternalLink}, a NEET platform serving 100+ daily users.
  \item Developed 20+ responsive UI components and implemented Google authentication for 1K+ users.
  \item Scaled the platform to 1000+ users within 3 months, achieving a 4.7/5 user satisfaction score.
\end{itemize}

\vspace{2pt}

\textbf{EXEEVO} \\
\textit{AI/ML Engineering Intern} \hfill \textit{Jan 2026 -- Present}
\begin{itemize}
\item Built an AI-powered Configuration Assistant to automate Exeevo and Dynamics 365 feature setup.
  \item Implemented Azure AD (PKCE) authentication with role-based access and system reliability improvements.
  \item Developed LLM-based natural language configuration using semantic embeddings and similarity search.
\end{itemize}

% === TECHNICAL SKILLS ===
\vspace{6pt}
\section*{Technical Skills}
\rule{\linewidth}{0.4pt}
\begin{flushleft}
\textbf{Programming Languages:} Java, C, Python, JavaScript, TypeScript, SQL, HTML, CSS \\
\textbf{Frameworks \& Libraries:} Node.js, Express.js, React.js, Next.js, Redux, TailwindCSS, Bootstrap \\
\textbf{Tools \& Platforms:} Git, GitHub, Docker, Postman, MySQL, PostgreSQL, MongoDB, NoSQL \\
\textbf{Development Skills:} API Development, Full-Stack Web Development, Containerization, CI/CD \\
\textbf{Software \& OS:} Linux, Windows, VSCode, Google Cloud Console \\
\textbf{AI \& ML:} Large Language Models (LLM), Generative AI, Machine Learning, NumPy \\
\textbf{Relevant Coursework:} Computer Architecture, Operating Systems, Cyber Security, Networking, DBMS
\end{flushleft}

% === ACHIEVEMENTS AND CERTIFICATIONS ===
\vspace{6pt}
\section*{Achievements and Certifications}
\rule{\linewidth}{0.4pt}

% --- Achievements ---
\begin{itemize}[leftmargin=1.2em, itemsep=2pt, topsep=0pt, parsep=0pt]
  \item Runners-up in Intercollege PBL Competition for Library Management System project.
  \item Solved 500+ Data Structures and Algorithms (DSA) problems across LeetCode, Codeforces, and GFG.
  \item Published 50+ solutions on LeetCode Discuss, with 3500+ views and community engagement.
  \item Google Cloud Skills Boost – Bronze League (Member since 2023)~\href{https://www.cloudskillsboost.google/public_profiles/fa563759-0891-4a0a-ba22-a0ea94817ef7}{\faExternalLink}
\end{itemize}


% --- Certifications ---
\vspace{4pt}
\textbf{Certifications:}
\begin{itemize}[leftmargin=1.2em, itemsep=4pt, topsep=2pt, parsep=0pt]
  \item \begin{tabular*}{\linewidth}{@{\extracolsep{\fill}} ll}
       Micro1 AI/ML Engineering Intern~\href{https://drive.google.com/file/d/1CufvoYjjeAuTnyfZEbQUCOKUBJmjG8-q/view}{\faExternalLink} &  
      $\bullet$ Cyber Threat Management – Cisco Networking Academy~\href{https://drive.google.com/file/d/12qL1hh5b7fOOVJBatiCHL9-LgfsoEUBZ/view?usp=drive_link}{\faExternalLink} \\
  \end{tabular*}

  \item \begin{tabular*}{\linewidth}{@{\extracolsep{\fill}} ll}
       Data \& ML in Manufacturing – AWS Industry Program~\href{https://drive.google.com/file/d/1C7YLJ9KqivkvSNi7VuHsaYZ3TOZZBRHF/view?usp=drive_link}{\faExternalLink} & 
      $\bullet$ Cyber Job Simulation – Deloitte (Forage)~\href{https://drive.google.com/file/d/1YNllN9Gum55uhvf3mcXfbETkr1ym-XtC/view?usp=drive_link}{\faExternalLink} \\
  \end{tabular*}
\end{itemize}

\end{document}
